%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Template
% Version 1.2 (25/3/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking}  % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}     % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{filecontents}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.80]{geometry}  % Reduce document margins

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Maïmouna} % Your first name
\familyname{BOCOUM} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{18 rue du 14 juillet}{Kremlin-Bicêtre, France}
\mobile{(+33) 6 14 06 41 50}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{maimouna.bocoum@espci.fr}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{French Driving Licence}
%\extrainfo{Date of birth: 01-27-1989}
%\photo[70pt][0.4pt]{pictures/picture.png} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

%% To remove the cover letter, comment out this entire block
%
%\clearpage
%
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[1-3] % Dummy text
%
%\makeletterclosing % Print letter signature
%
%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2012--2016}{Doctorate}{Ecole Polytechnique}{Paris}{}{Femtosecond lasers and plasma physics}
\cventry{2012}{Master Degree}{Ecole Polytechnique- UPMC}{Paris}{}{Nuclear Fusion Program}  % Arguments not required can be left empty
\cventry{2009--2012}{Engineering degree}{ENSTA Paristech}{Paris}{}{Specialized in physics and mathematics}

\section{PhDThesis}

\cvitem{Title}{High-order harmonic and electron beams from plasma mirrors}
\cvitem{Supervisors}{Professor Lopez-Martens}
\cvitem{Description}{Experimental work on the generation of intense XUV radiation and electron beams from plasmas driven with intense femtosecond laser pulses. My work consisted in setting up the experiment, analyzing the data and working together with theoreticians on the interpretation of experimental results.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Research experience}

%------------------------------------------------
\cventry{2019-2020}
{Young-Researcher}
{\textsc{Institut Langevin-CNRS}}
{Paris}
{}
{Laureate of young researcher CNRS recruitment campaign in 2018. Research area: development of  Acousto-Optic (AO) imaging for \textit{in-vivo} applications. Development of a digital holographic setup for the detection of tagged light.}


\cventry{2017-2018}
{Post-Doctorate}
{\textsc{Institut Langevin-INSERM}}
{Paris}
{}
{Development of Acousto-Optic imaging prototype for medical imaging in the scope of MALT Plan Cancer project. Experimental work on photorefractive and hold-burning filtering. Theoretical work on acoustic beam forming.}

\cventry{2016-217}
{Post-Doctorate}
{\textsc{Laboratoire d'Optique Appliquée}}
{Palaiseau}
{}
{Experimental working on high-order harmonic generation in continuity of PhD}

\cventry{2012--2016}{PhD}
{%institution
\textsc{Laboratoire d'Optique Appliquée}}
{%location
Palaiseau}
{}
{% details of the work
Detailed achievements:
Experimental PhD work on high-order harmonic generation from relativistic plasma mirrors: femtosecond pump-probe metrology, X-UV spectroscopy, fast electron detection and spectrometry, few cycle pulse metrology, kHz solid target metrology, design of a post-compression chamber, computer interface of experimental set-up, data analysis and analytical/numerical modeling. 
}

%------------------------------------------------

\cventry{2012}
{Master internship}
{\textsc{Laboratoire d'Utilisation des Lasers Intenses}}
{Palaiseau}
{}
{Experimental part in a time-resolved pump-probe diffraction campaign to study the iron phase transition at high radiation pressures. }

%------------------------------------------------



\cventry{2010}{Summer internship}{\textsc{Polytechnique of Montreal}}
{Quebec}
{}
{Experimental characterization of charge transport mechanism in melanin. Theoretical work on tetracene growth and polycrystalline properties.}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Grants and awards}

\cvitem{2012}{PHD scolarship from ENSTA-Paritech}
\cvitem{2014}{Best junior presentation award at the "International Conference on Ultra Intense Lasers", Goa-India}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{\textsc{C/C++}, html , Linux}
\cvitem{Intermediate}{LaTeX, Solidworks}
\cvitem{Advanced}{Matlab, Labview}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Teaching experience}

\cvitem{2018 - 2020}{Teacher assistant at ESPCI in optics (10 hours/year)}
\cvitem{2012 - 2020}{Teacher assistant at ENSTA ParisTech in Quantum mechanics for first year engineer students  (24 hours / year) }
\cvitem{2012 - 2016}{Teacher assistant at ENSTA ParisTech in Non-linear optics for second year students  (22 hours / year)}
\cvitem{2008 – 2009}{Mathematics examiner for preparatory classes at Michelet High School, Paris. Employer: French Education  }

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{French}{Mothertongue}{}
\cvitemwithcomment{English}{Fluent}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{List of publications}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\begin{itemize}
\item J. Wünsche, G. Tarabella, S Bertolazz, \textbf{M.Bocoum} et al. "The correlation between gate dielectric, film growth, and charge transport in organic thin film transistors: the case of vacuum-sublimed tetracene thin films."  \textbf{Journal of Materials Chemistry C}  1.5, pp967-976  (2013) 

\item W. Okell, T. Witting, D. Fabris, D. Austin, \textbf{M.Bocoum} and al. "Carrier-envelope phase stability of hollow fibers used for high-energy few-cycle pulse generation." \textbf{Optics letters} 38. pp3918-3021 (2013)

\item A. Denoeud, N. Osaki, A.Benuzzi-Mounaix, H. Uranishi, Y. Kondo, R. Kodamac, E. Brambrink, A. Ravasio, \textbf{M. Bocoum} and al. "Dynamic X-ray diffraction observation of shocked solid iron up to 170 GPa” \textbf{PNAS} 113.28 pp7745-7749 (2016)

\item \textbf{M. Bocoum} and al. "Practical spatial phase shift imaging interferometer for femtosecond characterization of plasma mirrors” \textbf{Optics letters} 40 pp3009-30012 (2015)

\item B. Beaurepaire, A. Vernier, \textbf{M.Bocoum} and al. "Effect of the laser wave front in a laser-plasma accelerator.” \textbf{Physical Review X} pp.031012. (2015)

\item \textbf{M. Bocoum}  and al.. "Anticorrelated emission of high-order harmonics and fast electron beams for relativistic plasma mirrors”  \textbf{Physical Review Letters} 116.18” pp.185001  (2016)

\item  D. Guénot, D. Gustas, A. Vernier, B. Beaurepaire, F. Böhle, \textbf{M. Bocoum} and al. "Relativistic electron beams driven by kHz” \textbf{Nature Photonics} 11 pp293-296 (2017)

\item ...\textbf{M.Bocoum} (30's author on 42), “The eli-alps facility : the next generation of attosecond sources,” Journal of Physics B : Atomic, Molecular and Optical Physics vol.50 no.13 pp132002 (2017)

\item  \textbf{M. Bocoum} and al. “Two-color interpolation of absorption response for quantitative acousto-optic imaging,” \textbf{Optics letters} 43(3), 399-402 (2017)

\item  C.Venet, \textbf{M. Bocoum} et al. “Ultrasound-modulated optical tomography in scattering media: flux filtering based on persistent spectral hole burning in the optical diagnosis window” \textbf{Optics letters} 43(16), 3993-3996 (2018)

\item  \textbf{M. Bocoum} and al. “Laser wakefield acceleration driven by few-cycle pulses on plasma mirrors” \textbf{Applied Optics} 58(8), 1933-1940 (2019)

\item  N.Zaim, F.Bohle,\textbf{M. Bocoum} and al. “Structured ultrasound-modulated optical tomography” \textbf{Physics of Plasma} 26(0), 033112 (2019)

\item  M.Ouillé, A.Vernier, F.Böhle, \textbf{M. Bocoum} and al. “Relativistic-intensity near-single-cycle light waveforms at kHz repetition rate” \textbf{Light: Science \& Applications} 9(1), 1-9 (2020)


\end{itemize}

%----------------------------------------------------------------------------------------

\end{document}